%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Project Name : HyperPath                                            %
% Project Home : https://github.com/TeamAC/HyperPath                  %
% Part         : State of the art in the field                        %
% Author       : chedi                                                %
% Comments     :                                                      %
%                                                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{State of the art}
\subsection{Geomarketing}
Is an advanced type of study that links a database to digital maps, with
practical applications in the marketing field. The research offers new types of
data analysis that can be applied to different domains : evaluating the
suitability of a site, finding new opportunities as well as identifying the
customers' geographical distribution in reference to a certain point of sale.
This information management system combines geographical and socio-demographic
data, both exclusive to Ipsos-Stat, translating them into comprehensive maps and
showing the correlation between the locations and the different variables understudy.

\subsection{Geomarketing applications}
Geomarketing applications are crucial in the decision making processes of
various businesses : the primary areas can be identified as retail / wholesale
trade, in which Geomarketing helps to better identify the customers and their
spending habits and study the site analysis and the existence of potential
clients in specific trade zones. Geomarketing can benefit finance and insurance
companies by helping them implement market share and competition analysis,
evaluate their branch locations, identify new markets as well as study the
demographic trends in an area. Geomarketing can help transportation and
distribution institutions to optimize performance and reduce operating costs.

Cartography is currently revolutionising the way businesses operate, not just
because of its ability to illustrate, but because it can produce meaningful and
immediate interpretations of complex analyses involving many variables. On a
single map, information from a variety of sources can be juxtaposed in layers to
reveal correlations with a simple mouse click, for faster search and analysis
operations.

\section{Solution}
