%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Project Name : HyperPath                                            %
% Project Home : https://github.com/TeamAC/HyperPath                  %
% Part         : BIRT introduction section                            %
% Author       : chedi                                                %
% Comments     :                                                      %
%                                                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction to BIRT}\index{Birt!Introduction}
\subsection{Introduction to business intelligence}

To give it a formal definition I would say that business intelligence is any tool or method that allows developers to take data or information, process it, manipulate it, and associate it with related information and present it to decision makers. As for a simplified definition, it's presenting information to decision makers in a way that helps them make informed decisions.

\subsection{The Current State of the BI Market}
you can divide the major players in this field into two categories: commercial offerings and open-source offerings. Each category has its own benefits and drawbacks. With the commercial offerings, typically you have familiar names such as Actuate and Business Objects,offering various tools aimed at different levels of business. Some of these tools are large and enterprise reporting platforms that have the ability to process,analyze, and reformat large quantities of data. One of the drawbacks of commercial offerings is the large price associated with them, both in terms of purchasing and in terms of running them.

Then, you have your open-source offerings. Currently there are three big names in the open-source reporting realm: JasperReport, Pentaho, and BIRT. Two of these projects, JasperReports and BIRT, are run by commercial companies who make their money by doing professional services for these offerings to small scale and private projects. Again, there are a number of pros and cons associated with open-source solutions. With open-source, you have full access to the source code of the platform you choose. This allows you to add in functionality, embed it with your existing applications, and actively participate in a development community that is oftentimes very large and around the world. There is little initial cost to open-source software in terms of purchasing, as open-source is free. The cons are that there is typically a cost associated with finding individuals who are knowledgeable in open-source.

\subsection{What is BIRT ?}
BIRT (which stands for Business Intelligence and Reporting Tools) is actually a development framework. Adding the word "Tools" to the title acronym is appropriate; BIRT is in fact a collection of development tools and technologies, used for report development, utilizing the BIRT framework. BIRT isn't necessarily a product, but a series of core technologies that products and solutions are built on top of, similar in fashion to the Eclipse framework.

\subsection{Why BIRT?}
As mentioned before, there are other open-source reporting platforms out there.So what makes BIRT stand out over JasperReports or Pentaho? With JasperReports, in reality, it comes down to tastes. I prefer the "What You See Is What You Get" (WYSIWYG) designer of BIRT over JasperReports. I also like the fact that it does not require compiling of reports to run, and that it is an official Eclipse project. However, that is not to say Jasper is not without strengths of its own. Jasper does do pixel-perfect rendering of reports, which is something that BIRT does not do. Later
versions of Jasper also support the Hibernate HQL language.