%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Project Name : HyperPath                                            %
% Project Home : https://github.com/TeamAC/HyperPath                  %
% Part         : MySQL introduction section                           %
% Author       : chedi                                                %
% Comments     :                                                      %
%                                                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{MySQL}
\subsection{Introduction}\index{MySQL!Introduction}
In today's interconnected world, it's almost impossible to find a business that doesn’t depend on information in some form or another. Be it marketing data, financial movements, or operational statistics, businesses today live or die by their ability to manage, massage, and filter information flow in order to achieve a competitive advantage.

More often than not, all this data finds a home in a business’ relational database management system (RDBMS), a software tool that assists in organizing, retrieving, and cross-referencing information. A large number of such systems are currently available, and you’ve probably already heard of some of them: Oracle, Sybase,Microsoft Access, and PostgreSQL are well-known names. These database systems are powerful, feature-rich software applications, capable of organizing and searching millions of records at high speeds; as such, they’re widely used by businesses and government offices, often for mission-critical purposes.

Recently, though, more and more attention has focused on a relatively new entrant in this field: MySQL. MySQL is a high-performance, multithreaded, multiuser RDBMS built around a client-server architecture. Over the last few years, this fast, robust, and user-friendly database system has become the de facto choice for both business and personal use, notably on account of its advanced suite of data management tools, its friendly licensing policy, and its worldwide support community of users and engineers. This introductory chapter will gently introduce you to the world of MySQL by taking you on a whirlwind tour of MySQL’s history, features, and technical architecture.

\subsection{Top Reasons to Use MySQL}\index{MySQL!Advantages}

\begin{description}
\item[Scalability and Flexibility :] \index{MySQL!Advantages!Scalability}
The MySQL database server provides the ultimate in scalability, sporting the capacity to handle deeply embedded applications with a footprint of only 1MB to running massive data warehouses holding terabytes of information.

\item[High Performance :]\index{MySQL!Advantages!Performance}
A unique storage-engine architecture allows database professionals to configure the MySQL database server specifically for particular applications, with the end result being amazing performance results. With high-speed load utilities, distinctive memory caches, full text indexes, and other performance-enhancing mechanisms, MySQL offers all the right ammunition for today's critical business systems.

\item[Web and Data Warehouse Strengths :]\index{MySQL!Advantages!Data warehousing}
MySQL is the de-facto standard for high-traffic web sites because of its high-performance query engine, tremendously fast data insert capability, and strong support for specialized web functions like fast full text searches. These same strengths also apply to data warehousing environments where MySQL scales up into the terabyte range for either single servers or scale-out architectures.

\item[Comprehensive Application Development :]\index{MySQL!Advantages!Development}
One of the reasons MySQL is the world's most popular open source database is that it provides comprehensive support for every application development need. Within the database, support can be found for stored procedures, triggers, functions, views, cursors, ANSI-standard SQL, and more. MySQL also provides connectors and drivers (ODBC, JDBC, etc.) that allow all forms of applications to make use of MySQL as a preferred data management server. It doesn't matter if it's PHP, Perl, Java, Visual Basic, or .NET, MySQL offers application developers everything they need to be successful in building database-driven information systems.

\item[Management Ease :]\index{MySQL!Advantages!Management}
MySQL offers exceptional quick-start capability with the average time from software download to installation completion being less than fifteen minutes. This rule holds true whether the platform is Microsoft Windows, Linux, Macintosh, or UNIX. Once installed, self-management features like automatic space expansion, auto-restart, and dynamic configuration changes take much of the burden off already overworked database administrators. MySQL also provides a complete suite of graphical management and migration tools that allow a DBA to manage, troubleshoot, and control the operation of many MySQL servers from a single workstation.

\item[Open Source Freedom:]\index{MySQL!Advantages!Freedom}
Pure awesomeness !
\end{description}
