%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Project Name : HyperPath                                            %
% Project Home : https://github.com/TeamAC/HyperPath                  %
% Part         : Anstract                                             %
% Author       : chedi                                                %
% Comments     :                                                      %
%                                                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
\emph
{
  ``Computers have traditionally lacked the ability to influence and be
  influenced by the surrounding environment. With the growth of location sensitive
  services and applications, the physical and the virtual are merging. Location
  based computing is becoming real thanks to advances in mobile devices, wireless
  connectivity and location detection technologies''
}\cite{geolocation:edventure}
\\
\\
A city offers thousands of social events and service promotions a day, and it is
difficult to make choices or even to be aware of all of them. The combination of
mobile phones and recommender systems can change the way one deals with such
abundance. Mobile phones with positioning technology are now widely available,
making it easy for service to broadcast their whereabouts. Recommender systems
can now identify patterns in people’s movements in order to, for example,
recommend events.
\\
\\
To answer this question, we try to build a mini management platform around
various business services and social events in a large metropolitan area. We
sample location estimations and combine the sample with services in the same
area. Upon this data, we extract statistics and reports displaying consumers
behaviours.
\\
\\
\emph
{
  ``Basically, all the world around you is going to be in geo-coded databases,
  and you’re going to be walking through these electronic yellow pages.''
}\cite{geolocation:edventure}
\\
\\
To achieve these goals and with the main constraint being the usage of the Java
programming we decided to use a complete Open Source software development stack
composed from:
\begin{itemize}[topsep=0pt, partopsep=0pt, itemsep=1pt, parsep=1pt]
\item MySQL database
\item GlassFish java application server
\item Eclipse RCP for the front end application
\item Google Android for the mobile client
\end{itemize}
\end{abstract}